### 2021-10-04 README.Rmd
add CSV file of transmission probabilities and update README with data and plot example

>>>>

### eyre_transmission_probabilities

```{r eyre-transmission-probabilities}
eyre_transmission_probabilities

library(ggplot2)
library(stringr)
library(dplyr)
eyre_transmission_probabilities %>%
   group_by(
     setting,
     case_age_5y,
     contact_age_5y
   ) %>%
   summarise(
     across(
       probability,
       mean
     ),
     .groups = "drop"
   ) %>%
   rename(
     case_age = case_age_5y,
     contact_age = contact_age_5y
   ) %>%
   mutate(
     across(
       ends_with("age"),
       ~ factor(.x,
                levels = str_sort(
                  unique(.x),
                  numeric = TRUE
                )
       )
     )
   ) %>%
   ggplot(
     aes(
       x = case_age,
       y = contact_age,
       fill = probability
     )
   ) +
   facet_wrap(~setting) +
   geom_tile() +
   scale_fill_viridis_c() +
   coord_fixed() +
   theme_minimal() +
   theme(
     axis.text = element_text(angle = 45, hjust = 1)
   )

```
